Topological Equivariant Artist Model for Visualization Library Architecture

### 2023-06-02 paper/main.tex
fiber

%In a \textit{non-trivial} bundle fibers are isomorphic $\dfiber \simeq \dfiber_{\dbasepoint}$ for all points $\dbasepoint \in \dbase$ such that there is at least one transition map that is not an identity \cite{hatcherAlgebraicTopology2002}. For example, in the mobius band case, while $\dfiber_{0}\restriction_{[{\frac{2\pi}{5}}^{-}, {\frac{2\pi}{5}}^{+}]} = \dfiber_{0}\restriction_{[{\frac{2\pi}{5}}^{-}, {\frac{2\pi}{5}}^{+}]}$ such that the transition map is an identity map $\uparrow\rightarrow\uparrow$, the transition map must flip  $\uparrow \rightarrow \downarrow$ the fibers of $\dfiber_0\restriction_{[\epsilon^{-}, \epsilon^{+}]}$ in order for them to be equal to the fibers of $\dfiber_1\restriction_{[\epsilon^{-}, \epsilon^{+}]}$.

@@

The fiber category $\mathcal{\dfiberc}$ is also equipped with a bifunctor because it is a monoidal category and this functor provides a method for combining fiber types. The bifunctor $\otimes: \mathcal{\dfiber} \times \mathcal{\dfiber} \rightarrow \mathcal{\dfiber}$ allows us to express fields that contain multityped values. For example, wind can be represented as two fields $\dfiber_{speed} \times \dfiber_{direction}$ or a composite fiber field $\dfiber_{speed} \otimes \dfiber_{direction} = \dfiber_{wind}$. The $\otimes$ encapsulates both the sets associated with each fiber $\mathbb{R} \times \mathbb{R} = \mathbb{R}^{2}$ and the morphisms associated with each functor $(\dfunct_{speed}, \dfunct_{direction}) = \dfunct_{wind}$. Defining the field schema as a monoidal category allows us to formally express the structure of the field, as defined by its sets and functions, at different levels of composition as needed by different visualization tasks.
 \
\subsubsection{Data: Section} 
\label{sec:atct:fb:sections}
We encode data as a \textcolor{section}{section} \dsectionc\ of a bundle because this allows us to incorporate the topology and field types in the data definition. We can define these section functions locally, meaning that the section is (piece-wise) continuous over a specific open subset \openset\ of \dbase\
\begin{equation}
  \label{eq:atct:fb:sections}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\} 
\end{equation}
such that each section function $\dsection: \dbasepoint \mapsto \delement$ maps from each point $\dbasepoint \in \openset$ to a corresponding record in the fiber space $\delement \in \dfiber_{\dbasepoint}$ over that point. Bundles can have multiple sections, as denoted by $\Gamma(\openset, \dtotal\restriction{\openset})$. We can therefore model data as structures that map from an index like point $\dbasepoint$ to a data record $\delement$, and encapsulate multiple datasets with the same fiber and base space as different sections of the same bundle.

@@

\subsubsection{Multiplication}
\label{sec:artist:operator:multiplication}
\note{fiber product vs cartesian product}
As illustrated in \autoref{eq:artist:operator},  fibers that are a cartesian product of fiberspaces $\dfiber^{a} \times_{\dfiber^c} \dfiber^{b}$, where $\dfiber^c$ is any fiber that is present in both fibers, can be projected down into component fibers.
\begin{tikzcd}
  \dfiberc^{a}\times_{\dfiber^{c}} \dfiberc^{b} \arrow[d, "\pi_a"] \arrow[r, "\pi_b"] & \dfiberc^{b} \arrow[d, "\pi_c"] & {(temperature, time) \times_{time} (pressure, time)} \arrow[d, "\pi_a"] \arrow[r, "\pi_b"] & {(pressure,time)} \arrow[d, "\pi_c"] \\
  \dfiberc^{a} \arrow[r, "\pi_c"]                                                     & \dfiberc^{c}                    & {(temperature,time)} \arrow[r, "\pi_c"]                                                    & time                                
  \end{tikzcd}
In the trivial case where the base spaces are the same $\dbase^{a} = \dbase^{b} = \dbase$, this is equivalent to adding more fields to a dataset.

>>>>

@@

The fiber category $\mathcal{\dfiberc}$ is also equipped with a bifunctor because it is a monoidal category and this functor provides a method for combining fiber types. The bifunctor $\otimes: \mathcal{\dfiber} \times \mathcal{\dfiber} \rightarrow \mathcal{\dfiber}$ allows us to express fields that contain multityped values. For example, wind can be represented as two fields $\dfiber_{speed} \times \dfiber_{direction}$ or a composite fiber field $\dfiber_{speed} \otimes \dfiber_{direction} = \dfiber_{wind}$. The $\otimes$ encapsulates both the sets associated with each fiber $\mathbb{R} \times \mathbb{R} = \mathbb{R}^{2}$ and the morphisms associated with each functor $(\dfunct_{speed}, \dfunct_{direction}) = \dfunct_{wind}$. Combining fibers can be verified by checking that when a fiber component $\dfiber^{c}$ is present in both $\dfiber^{a}$ and $\dfiber^{b}$, it is identical when projected out of either such that the *product* diagram commutes:
\begin{minipage}

\begin{tikzcd}[c]{.25\columnwidth}
  \dfiberc^{a}\times_{\dfiber^{c}} \dfiberc^{b} \arrow[d, "\pi_a"] \arrow[r, "\pi_b"] & \dfiberc^{b} \arrow[d, "\pi_c"] & {(temperature, time) \times_{time} (pressure, time)} \arrow[d, "\pi_a"] \arrow[r, "\pi_b"] & {(pressure,time)} \arrow[d, "\pi_c"] \\
  \dfiberc^{a} \arrow[r, "\pi_c"]                                                     & \dfiberc^{c}                    & {(temperature,time)} \arrow[r, "\pi_c"]                                                    & time                                
  \end{tikzcd}
\end{minipage}\hfill
\begin{minipage}[c]{.65\columwidth}

\end{minipage}

This means that when multifield data is decomposed into its component fields, shared records stay the same. For example, the red (temperature, time, pressure) record seperates into (tempereture, time) and (pressure, time) records that share the same red time. Furthermore this time is the same whether it is obtained from the (temperature, time) or (pressure, time) record. This simple test that fields are joined together correctly for the same record is what allows us to reliably combine multiple datasets together on shared properties-for example growing the weather station data from a temporal to spatial dataset by adding the weather at each  location at each time.

\subsubsection{Data: Section} 
\label{sec:atct:fb:sections}
We encode data as a \textcolor{section}{section} \dsectionc\ of a bundle because this allows us to incorporate the topology and field types in the data definition. We can define these section functions locally, meaning that the section is (piece-wise) continuous over a specific open subset \openset\ of \dbase\
\begin{equation}
  \label{eq:atct:fb:sections}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\} 
\end{equation}
such that each section function $\dsection: \dbasepoint \mapsto \delement$ maps from each point $\dbasepoint \in \openset$ to a corresponding record in the fiber space $\delement \in \dfiber_{\dbasepoint}$ over that point. Bundles can have multiple sections, as denoted by $\Gamma(\openset, \dtotal\restriction{\openset})$. We can therefore model data as structures that map from an index like point $\dbasepoint$ to a data record $\delement$, and encapsulate multiple datasets with the same fiber and base space as different sections of the same bundle.

@@

\subsubsection{Multiplication}
\label{sec:artist:operator:multiplication}
\note{fiber product vs cartesian product}

In the trivial case where the base spaces are the same $\dbase^{a} = \dbase^{b} = \dbase$, this is equivalent to adding more fields to a dataset.
